---
title: "Data Description"
author: "H. LUSTIGER"
date: "Sunday, May 10, 2015"
geometry: margin=1.5cm
output:
  pdf_document:
      fig_height: 4
      fig_width: 10
      highlight: tango
---
        
```{r global_options, include=FALSE, echo=FALSE}
require(knitr)
opts_chunk$set(fig.width=8, fig.height=4, fig.path='figs/', dpi=500,
               echo=FALSE, warning=FALSE, message=FALSE, results='hide')
```

```{r pandoc_options, include=FALSE, echo=FALSE}
require(pander)
panderOptions('table.split.table', Inf)
panderOptions('digits', 3)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)
# performance.table <- table(some_table)
# pandoc.table(performance.table, style = "rmarkdown", justify = 'left', caption = 'Performance table') 
```

```{r load_the_data, cache=FALSE}
train <- read.csv("../data/train.csv.gz")   
set.seed(2014)
inTrain <- sample(1:nrow(train),round(0.7*nrow(train)))
```

<http://www.kaggle.com/c/afsis-soil-properties/data>
        
# Dependent Variables
        
`SOC`, `pH`, `Ca`, `P`, `Sand` are the five target variables for predictions.
The data have been monotonously transformed from the original measurements and
thus include negative values. 

```{r, results='asis'}
c1 <- c("[,3596]","[,3597]","[,3598]","[,3599]","[,3600]")
c2 <- c("Ca","P","pH","SOC","Sand")
c3 <- c("Mehlich-3 extractable Calcium","Mehlich-3 extractable Phosphorus",
        "pH values","Soil organic carbon","Sand content")
y.table <- data.frame("Col #"=c1,"Variable"=c2,"Description"=c3)
pandoc.table(y.table, style = "simple", justify = 'left')#, 
             #caption = "Dependent Variables") 
```

        
```{r DD_Ycorr, results='markup', eval=TRUE, fig.height=4, fig.width=8}
require(corrplot)
corrplot(cor(
        subset(train[inTrain,], select=Ca:Sand)), method = "circle",
        mar = c(0,0,2,0), type = "lower",
        title = "A visualization of the 5 dependent variables correlation matrix")
```

\newpage

# Predictors Variables

```{r, results='asis'}
c1 <- c("[,1]")
c2 <- c("PIDN")
c3 <- c("Unique soil sample identifier")
ID.table <- data.frame("Col #"=c1,"Variable"=c2,"Description"=c3)
pandoc.table(ID.table, style = "simple", justify = 'left')#, 
             #caption = "Dependent Variables") 
```
        
## Infrared Spectrom Variables Group 

[Near-infrared (NIR) spectroscopy][NIR] is a technique that measures the amount
of heat absorbed or emitted by certain materials.

The data set contains 3,578 mid-infrared absorbance measurements in the
7500 to 600 [$cm^{-1}$] range (1333 to 16,667 [$nm$]).
We suggest you to remove spectra CO2 bands which are in the region m2379.76 to
m2352.76, but you do not have to.

```{r, results='asis'}
c1 <- c("[,2-3579]")
c2 <- c("m7497.96 - m599.76")
c3 <- c("mid-infrared absorbance measurements")
X1.table <- data.frame("Col #"=c1,"Variable"=c2,"Description"=c3)
pandoc.table(X1.table, style = "simple", justify = 'left')#, 
             #caption = "Dependent Variables") 
```

        
## Spatial Variables Group
        
We have also included some potential spatial predictors from remote sensing data 
sources.
Short variable descriptions are provided below and additional descriptions can
be found at [AfSIS data](http://www.africasoils.net/data/datasets).
The data have been mean centered and scaled.

```{r, results='asis'}
c1 <- c("[,3580]","[,3581]","[,3582]","[,3583]","[,3584]","[,3585]","[,3586]",
        "[,3587]","[,3588]","[,3589]","[,3590]","[,3591]","[,3592]","[,3593]",
        "[,3594]","[,3595]")
c2 <- c("BSAN","BSAS","BSAV","CTI","ELEV","EVI","LSTD","LSTN","Ref1","Ref2",
        "Ref3","Ref7","Reli","TMAP","TMFI","Depth")
c3 <- c(
"Near-infraredaverage average long-term Black Sky Albedo measurements",
"Short-wave average long-term Black Sky Albedo measurements",
"Visible average long-term Black Sky Albedo measurements",
"Compound topographic index calculated from Shuttle Radar Topography Mission elevation data",
"Shuttle Radar Topography Mission elevation data",
"Average long-term Enhanced Vegetation Index from MODIS satellite images",
"Average long-term Land Surface Temperatures from MODIS satellite images (day time temperature)",
"Average long-term Land Surface Temperatures from MODIS satellite images (night time temperature)",
"Average long-term Reflectance measurements from MODIS satellite images (blue)",
"Average long-term Reflectance measurements from MODIS satellite images (red)",
"Average long-term Reflectance measurements from MODIS satellite images (near-infrared)",
"Average long-term Reflectance measurements from MODIS satellite images (mid-infrared)",
"Topographic Relief calculated from Shuttle Radar Topography mission elevation data", 
"Average long-term Tropical Rainfall Monitoring Mission data (mean annual precipitation)",     
"Average long-term Tropical Rainfall Monitoring Mission data (modified Fournier index)",     
"Depth of the soil sample (2 categories: 'Topsoil', 'Subsoil')")
X2.table <- data.frame("Col #"=c1,"Variable"=c2,"Description"=c3)
pandoc.table(X2.table, style = "simple", justify = 'left')#, 
             #caption = "Dependent Variables") 
```



\newpage

[NIR]: http://en.wikipedia.org/wiki/Near-infrared_spectroscopy